Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-07-30 paperIEEE.tex
Reviewer 1, Collage
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@137 db7c848b-7755-4df2-b763-8796797afa52

\fig{fLayout} shows RTT Deltagen running an example multi-segment, multi-view
setup driven by eight rendering nodes. The main tiled display wall canvas uses
four LCD segments showing one layout with four views, which do not align on the
segment boundaries. This setup creates seven destination channels. The
configuration provides multiple, run-time configurable layouts. It is driven
from the control host on the right, which shows four views, each in their own
canvas and segment windows with a single-view layout each. One view on the
control host synchronizes its content (model and camera) with one view on the
display wall through Collage objects. The control host allows full model
modifications and all workflows supported within the standalone Deltagen
application, and all changes are synchronized to the corresponding rendering
nodes. For this monoscopic setup no head tracking or observers are used.

@@

An important part of writing a parallel rendering application is the
communication layer between the individual processes. \textsf{Equalizer} relies
on the
\textsf{Collage} network library for its internal operation. \textsf{Collage}
furthermore provides
powerful abstractions for writing \textsf{Equalizer} applications, which are
introduced
in this section.

>>>>

\fig{fLayout} shows RTT Deltagen running an example multi-segment, multi-view
setup driven by eight rendering nodes. The main tiled display wall canvas uses
four LCD segments showing one layout with four views, which do not align on the
segment boundaries. This setup creates seven destination channels. The
configuration provides multiple, run-time configurable layouts. It is driven
from the control host on the right, which shows four views, each in their own
canvas and segment windows with a single-view layout each. One view on the
control host synchronizes its content (model and camera) with one view on the
display wall through \textsf{Collage} objects. The control host allows full
model modifications and all workflows supported within the standalone Deltagen
application, and all changes are synchronized to the corresponding rendering
nodes. For this monoscopic setup no head tracking or observers are used.

@@

An important part of writing a parallel rendering application is the
communication layer between the individual processes. \textsf{Equalizer} relies
on the \textsf{Collage} network library for its internal operation.
\textsf{Collage} furthermore provides powerful abstractions for writing
\textsf{Equalizer} applications, which are introduced in this section.
\textsf{Collage} is a separate, standalone library heavily influenced by the
requirements of \textsf{Equalizer}. It is used directly when implementing data
distribution for parallel rendering applications, and independently by a few
research projects.
